### 2023-10-05 main.tex
fix

We observe that, at most $q$ factors do survive in the product over $k$. Moreover, for a fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  

@@

For any $q\in\{1,\ldots,m\}$, we can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 

@@

Moreover, observing that 
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}

>>>>

We observe that, at most $q$ factors do survive in the product over $k$. For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  

@@

We can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 

@@

Moreover, we observe that 
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
